The Morality of Arbitrage

### 2017-04-23 Draft/draft2.Rmd
Updating draft2.

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ./svm-latex-ms.tex
title: "The Morality of Arbitrage"
author:
- name: Tyler J. Brough
  affiliation: Utah State University
abstract: "In this paper, I argue that one cannot rationally believe that financial arbitrage is an inherently immoral pursuit, while simultaneously believing that the pursuit of academic knowledge is an inherently moral pursuit. I argue that these two seemingly separate activities are really one and the same. Further those that do hold such contradictory beliefs are behaving incoherently and have a Dutch book made against them."
keywords: "arbitrage, Dutch books, morality"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
# spacing: double
bibliography: ./master.bib
biblio-style: apsr
---

>>>>

---
output: 
  pdf_document:
    citation_package: natbib
    keep_tex: true
    fig_caption: true
    latex_engine: pdflatex
    template: ./svm-latex-ms.tex
title: "The Morality of Arbitrage"
author:
- name: Tyler J. Brough
  affiliation: Utah State University
abstract: "In this paper, I argue that one cannot rationally believe that financial arbitrage is an inherently immoral pursuit, while simultaneously believing that the pursuit of academic knowledge is an inherently moral pursuit. I argue that these two seemingly separate activities are really one and the same. Further those that do hold such contradictory beliefs are behaving incoherently and have a Dutch book made against them."
keywords: "arbitrage, Dutch books, morality"
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 11pt
spacing: double
bibliography: ./master.bib
biblio-style: apsr
---

### 2017-04-23 Draft/draft2.tex
Updating draft2.

\noindent  \begin{quote}
{[}T{]}he shipper who earns his living from using otherwise empty or
half-filled journeys of tramp-steamers, or the estate agent whose whole
knowledge is almost exclusively one of temporary opportunities, or the
\emph{arbitrageur} who gains from local differences of commodity prices,
are all performing eminently useful functions based on special knowledge
of circumstances of the fleeting moment not known to others. -- F.A.
Hayek
\end{quote}

>>>>

\noindent \doublespacing \begin{quote}
{[}T{]}he shipper who earns his living from using otherwise empty or
half-filled journeys of tramp-steamers, or the estate agent whose whole
knowledge is almost exclusively one of temporary opportunities, or the
\emph{arbitrageur} who gains from local differences of commodity prices,
are all performing eminently useful functions based on special knowledge
of circumstances of the fleeting moment not known to others. -- F.A.
Hayek
\end{quote}
